%-------------------------
% Cover letter in LaTeX -- one page, clean business-letter style.
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}         % paragraph spacing instead of indents
\usepackage[english]{babel}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\pagestyle{empty}

\begin{document}

%---------- SENDER ----------
\begin{center}
    {\Large \scshape Dhruvkumar Patel}\\[2pt]
    \small Vancouver, BC $|$ (672) 553-1105 $|$ \href{mailto:dhruvv.patel@outlook.com}{dhruvv.patel@outlook.com} $|$
    \href{https://www.linkedin.com/in/dhruvkumarpatell/}{LinkedIn} $|$ \href{https://dhruvvkumarpatel.vercel.app/}{Portfolio}
\end{center}

\vspace{8pt}
July 8, 2026

\vspace{4pt}
Hiring Team\\
PEAK Products Manufacturing

\vspace{8pt}
Dear Hiring Team,

I am applying for the Senior Inventory Analyst role in Richmond. I currently run daily inventory operations for a warehouse serving roughly 300 Save-On-Foods retail stores, and I hold a Master of Professional Studies in Data Analytics. That combination, hands-on inventory work plus demand-forecasting and reporting skills, is exactly what your role asks for, and PEAK's distribution model across Home Depot and Bunnings is the kind of retail supply environment I want to grow in.

Inventory accuracy and continuity of supply are what I do every day. I manage cycle counts and audits across 200+ orders daily, reconcile overages, shortages, and damaged goods, and validate incoming deliveries against bills of lading and packing slips so system orders close cleanly and records stay current. I coordinate weekly interbranch shipments and backorder communications with logistics and store teams to keep product available across locations and head off stockouts, and I prepare daily KPI reports on inventory accuracy, fulfillment rate, and shipping performance so operations can plan and replenish with real numbers. This is the same maintain-availability, coordinate-across-teams, report-to-management work described in your posting.

On the forecasting side, my capstone project built a weighted ensemble model (Random Forest, XGBoost, and LightGBM) on 183,909 records that reached 84.7\% accuracy and cut forecast error by 28\%, giving operations planners demand visibility before shortfalls hit. In a separate analytics project I consolidated 11 datasets into one analytical layer and automated stakeholder reporting into one-click Excel workbooks across 13 views, replacing manual spreadsheet prep. I want to be straightforward: my direct inventory tenure is a little over a year and my ERP work has been on warehouse inventory systems rather than SAP or NetSuite specifically. I ramp on new systems quickly, and I would bring proven forecasting, reconciliation, and reporting skill to PEAK from day one.

I would welcome the chance to talk about how my inventory operations experience and analytics background can support PEAK's purchasing and supply planning. Thank you for your consideration.

\vspace{8pt}
Sincerely,\\
Dhruvkumar Patel

\end{document}
