%-------------------------
% Resume in LaTeX  --  Jake's Resume (Overleaf), MIT License
% https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Dhruvkumar Patel} \\ \vspace{1pt}
    \small (672) 553-1105 $|$ \href{mailto:dhruvv.patel@outlook.com}{\underline{dhruvv.patel@outlook.com}} $|$
    \href{https://www.linkedin.com/in/dhruvkumarpatell/}{\underline{LinkedIn}} $|$
    \href{https://github.com/pateldhruvkumar}{\underline{GitHub}} $|$
    \href{https://dhruvvkumarpatel.vercel.app/}{\underline{Portfolio}} $|$
    Vancouver, BC
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{A supply chain and data analytics professional focused on demand forecasting, inventory accuracy, and cross-functional supply planning. Backed by hands-on warehouse inventory operations serving roughly 300 retail stores and a graduate data-analytics education, has built forecasting models reaching 84.7\% accuracy and cut operational order spend by thousands of dollars annually. Actively seeking a senior inventory analyst role in a manufacturing or distribution environment.}
  \vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Vancouver, BC}
      {Master of Professional Studies, Data Analytics (AI/ML Concentration)}{Jan 2025 -- Jun 2026}
    \resumeSubheading
      {Uka Tarsadia University}{Gujarat, India}
      {Bachelor of Technology, Information Technology -- Graduated with Distinction}{Aug 2019 -- Feb 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Jim Pattison Food Group (Save-On-Foods)}{Surrey, BC}
      {Warehouse Logistics Associate}{Mar 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Manage daily cycle counts and inventory audits across warehouse systems, reconciling overages, shortages, and damaged goods to keep inventory records accurate across 200+ orders daily serving roughly 300 retail stores.}
        \resumeItem{Validate incoming deliveries against bills of lading and packing slips and coordinate receiving documentation with carriers and suppliers, keeping system orders closed and inventory records current.}
        \resumeItem{Coordinate weekly interbranch shipment and backorder communications with logistics and store teams to maintain product availability across locations and prevent stockouts.}
        \resumeItem{Prepare daily KPI reports tracking inventory accuracy, fulfillment rate, and shipping performance to support operational planning and replenishment decisions.}
      \resumeItemListEnd

    \resumeSubheading
      {Northeastern University}{Vancouver, BC}
      {Operations Data Assistant}{Jan 2026 -- Jun 2026}
      \resumeItemListStart
        \resumeItem{Diagnosed and rewrote an inefficient cost-calculation query in the operations database, correcting pricing logic and cutting order spend by thousands of dollars annually.}
        \resumeItem{Built and optimized Power BI dashboards by refactoring DAX measures and calculated columns, reducing report refresh time 13\% and giving stakeholders faster operational visibility.}
        \resumeItem{Managed a 1,000+ record operations database, maintaining data accuracy and integrity to support operations reporting and daily planning workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Dots N Key}{Surat, India}
      {Software Developer}{Dec 2022 -- Jul 2024}
      \resumeItemListStart
        \resumeItem{Boosted query performance 60\% on a high-traffic retail POS platform by leading a full MySQL to AWS RDS migration, unlocking production-grade scalability for retail operations data.}
        \resumeItem{Maintained 99.9\% system uptime by deploying cloud infrastructure with real-time monitoring dashboards, catching and resolving incidents before end-user impact.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Charging Demand Forecast, Vancouver International Airport (Capstone)} $|$ \emph{Python, Random Forest, XGBoost, LightGBM}}{Jan 2026 -- Apr 2026}
          \resumeItemListStart
            \resumeItem{Engineered a weighted ensemble forecasting model (Random Forest, XGBoost, LightGBM) on 33 time, lag, flight, and weather features, reaching 84.7\% accuracy and cutting forecast error 28\%.}
            \resumeItem{Processed 183,909 sessions across 56 assets into a clean modeling dataset and delivered a 7-tab Streamlit dashboard surfacing demand and asset-health signals so planners could anticipate shortfalls before they hit operations.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Global Seaweed Market Analytics Dashboard} $|$ \emph{Python, DuckDB, Excel}}{Apr 2026 -- Jun 2026}
          \resumeItemListStart
            \resumeItem{Consolidated 11 datasets (33,000+ records) from FAO, Statistics Canada, and UN Comtrade into a single DuckDB analytical layer covering supply across 100+ countries, tracking KPIs like export value, price per tonne, and gross output.}
            \resumeItem{Automated stakeholder reporting with one-click Excel workbooks across 13 dashboard views, each carrying source citations and data-quality caveats, replacing manual spreadsheet prep.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Analytics \& Forecasting}{: Demand forecasting, time-series and ensemble modeling (Random Forest, XGBoost, LightGBM), KPI reporting, cost and variance analysis} \\
     \textbf{Data \& BI Tools}{: Microsoft Excel, Power BI (DAX), Streamlit, Plotly} \\
     \textbf{Databases \& Systems}{: SQL, MySQL, DuckDB, MongoDB, warehouse / inventory management systems, AWS (S3, RDS, Lambda)} \\
     \textbf{Programming}{: Python (pandas, NumPy, scikit-learn), SQL, JavaScript/TypeScript}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
