%-------------------------
% Cover letter in LaTeX -- one page, clean business-letter style.
% Tailored for: GymnO Laval -- Data Analyst
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}         % paragraph spacing instead of indents
\usepackage[english]{babel}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\pagestyle{empty}

\begin{document}

%---------- SENDER (from master-personal-info.md) ----------
\begin{center}
    {\Large \scshape Dhruvkumar Patel}\\[2pt]
    \small Vancouver, BC $|$ (672) 553-1105 $|$ \href{mailto:dhruvv.patel@outlook.com}{dhruvv.patel@outlook.com} $|$
    \href{https://www.linkedin.com/in/dhruvkumarpatell/}{LinkedIn} $|$
    \href{https://dhruvvkumarpatel.vercel.app/}{Portfolio} $|$
    \href{https://github.com/pateldhruvkumar}{GitHub}
\end{center}

\vspace{8pt}
July 7, 2026

\vspace{4pt}
Hiring Team\\
GymnO Laval

\vspace{8pt}
Dear Hiring Team,

I am applying for the Data Analyst role at GymnO Laval. The part of the posting that stood out is that insights here ``directly influence real business decisions'' across marketing, product, and operations. That is the kind of analysis I do best: taking raw data from several sources and turning it into dashboards and reports that people act on.

Your first responsibility is building and maintaining dashboards and reports in tools like Excel, SQL, and Power BI. As an Operations Data Assistant at Northeastern University, I did exactly that: I refactored DAX measures and calculated columns to cut a Power BI report's refresh time by 13\%, managed a student-records database of over 1,000 active students to keep operations reporting accurate, and rewrote an inefficient cost-calculation SQL query that corrected pricing logic and saved the university thousands of dollars a year. Those are small numbers on their own, but each came from a decision someone made off a cleaner report.

The posting also asks for cleaning, validating, and organizing data from multiple sources and presenting it clearly. For a market-intelligence dashboard, I consolidated 11 datasets and more than 33,000 records from FAO, Statistics Canada, and UN Comtrade into one analytical layer, then automated one-click Excel workbooks so non-technical stakeholders could pull the numbers, sources, and caveats themselves. I care about the caveats as much as the charts, since a report is only useful if the reader trusts what it does and does not say.

I am completing a Master's in Data Analytics and would bring Excel, SQL, and Power BI experience to your team from day one, plus a habit of explaining findings in plain language. I would welcome the chance to discuss how I can help GymnO Laval turn its data into decisions.

\vspace{8pt}
Sincerely,\\
Dhruvkumar Patel

\end{document}
