%-------------------------
% Cover letter in LaTeX -- one page, clean business-letter style.
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}         % paragraph spacing instead of indents
\usepackage[english]{babel}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\pagestyle{empty}

\begin{document}

%---------- SENDER ----------
\begin{center}
    {\Large \scshape Dhruvkumar Patel}\\[2pt]
    \small Vancouver, BC $|$ (672) 553-1105 $|$ \href{mailto:dhruvv.patel@outlook.com}{dhruvv.patel@outlook.com} $|$
    \href{https://www.linkedin.com/in/dhruvkumarpatell/}{LinkedIn} $|$ \href{https://dhruvvkumarpatel.vercel.app/}{Portfolio}
\end{center}

\vspace{8pt}
July 10, 2026

\vspace{4pt}
Hiring Team\\
TrendAI (Trend Micro)

\vspace{8pt}
Dear Hiring Team,

I am applying for the Applied AI Backend Engineer role (R0009942) on TrendAI Vision One. Building backend services that put AI into production is the work I have spent the last year doing, and I am ready to relocate to Ottawa and work on your hybrid, three-days-a-week schedule to do it on a security platform operating at real scale.

At Vault AI I architected an AI-powered client intake portal for private credit firms on Supabase and serverless Edge Functions, then built secure RAG pipelines over 100+ confidential documents with vector retrieval so the system stayed grounded and private on sensitive financial data. I also shipped an autonomous due-diligence agent that turns multi-source research into production-ready reports and fine-tuned Llama models with QLoRA to lift answer accuracy 15\%. That is the same combination your role calls for: AI-driven business logic, vector data stores, and backend services that have to be both secure and maintainable.

The scale and reliability side of the job is where my earlier work fits. At Dots N Key I led a full MySQL to AWS RDS migration that cut query time 60\% and removed a single point of failure, and I held 99.9\% uptime by running the platform on AWS EC2 and S3 with real-time monitoring dashboards, catching production incidents before they reached users. More recently I built a serverless ETL pipeline on AWS (Lambda, Glue, S3, DynamoDB) that ingests and deduplicates 5.6M records, and a text-to-SQL assistant on FastAPI and DuckDB with schema grounding and layered SQL-safety checks. Cloud-native services, APIs, data pipelines, and observability are already how I work.

I would welcome the chance to discuss how I can contribute to Vision One and to TrendAI's AI-first engineering culture. Thank you for your consideration.

\vspace{8pt}
Sincerely,\\
Dhruvkumar Patel

\end{document}
