%-------------------------
% Resume in LaTeX  --  Jake's Resume (Overleaf), MIT License
% https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% Left column is a wrapping p-column so a long project name + tech stack can
% never push the date past the right margin; the date is \small and right-aligned.
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{@{\extracolsep{\fill}}p{0.78\textwidth} r@{}}
      \small #1 & \small #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Dhruvkumar Patel} \\ \vspace{1pt}
    \small (672) 553-1105 $|$ \href{mailto:dhruvv.patel@outlook.com}{\underline{dhruvv.patel@outlook.com}} $|$
    \href{https://www.linkedin.com/in/dhruvkumarpatell/}{\underline{LinkedIn}} $|$
    \href{https://github.com/pateldhruvkumar}{\underline{GitHub}} $|$
    \href{https://dhruvvkumarpatel.vercel.app/}{\underline{Portfolio}} $|$
    Vancouver, BC
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{AI-focused software engineer building backend services and applied-AI systems: autonomous agents, RAG pipelines, and LLM text-to-SQL. Production experience on AWS with Node.js and FastAPI APIs, including a MySQL-to-RDS migration that cut query time 60\% at 99.9\% uptime. Seeking an applied AI backend engineering role.}
  \vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Vancouver, BC}
      {Master of Professional Studies, Data Analytics (AI/ML Concentration)}{Jan 2025 -- Jun 2026}
    \resumeSubheading
      {Uka Tarsadia University}{Gujarat, India}
      {Bachelor of Technology, Information Technology (Graduated with Distinction)}{Aug 2019 -- Feb 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vault AI}{Vancouver, BC}
      {Software Developer}{Jun 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Architected an AI client-intake portal on Supabase and serverless Edge Functions, adding natural-language analytics and automated extraction from unstructured PDFs.}
        \resumeItem{Built secure RAG pipelines over 100+ confidential documents with vector retrieval, and fine-tuned Llama models with QLoRA to improve answer accuracy 15\%.}
        \resumeItem{Engineered an autonomous due-diligence agent and extended Node/Express APIs across a 3-service monorepo with a 7-developer team (79 commits, Git PR workflow).}
      \resumeItemListEnd
    \resumeSubheading
      {Dots N Key}{Surat, India}
      {Software Developer}{Dec 2022 -- Jul 2024}
      \resumeItemListStart
        \resumeItem{Cut query time 60\% by leading the full MySQL to AWS RDS migration, removing a single point of failure and enabling production-scale growth.}
        \resumeItem{Held 99.9\% uptime on AWS EC2 and S3 with real-time monitoring dashboards, resolving production incidents before user impact.}
        \resumeItem{Lifted application performance 35\% through tuned React rendering, refactored Node.js logic, and optimized stored procedures.}
      \resumeItemListEnd
    \resumeSubheading
      {Unistar Softech}{Bardoli, India}
      {Software Developer}{May 2022 -- Nov 2022}
      \resumeItemListStart
        \resumeItem{Sped up backend processing 30\% by refactoring Node.js services and tuning database queries.}
        \resumeItem{Hardened security with Role-Based Access Control across 21 role tiers and integrated 45+ third-party APIs, cutting handoff delays 23\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Seaweed Market Intelligence Dashboard} $|$ \emph{FastAPI, DuckDB, Text-to-SQL, Embeddings}}{Apr 2026 -- Jun 2026}
          \resumeItemListStart
            \resumeItem{Engineered a text-to-SQL assistant on FastAPI and DuckDB where an LLM queries a 27,000-row dataset, grounded in the live schema and few-shot examples.}
            \resumeItem{Indexed roughly 41,000 entities with sentence embeddings and enforced SQL safety through parser validation, write-statement blocks, and error-fed retries.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AWS Big Data Pipeline -- Serverless ETL} $|$ \emph{AWS Lambda, Glue, S3, DynamoDB, Python}}{Jan 2026 -- Mar 2026}
          \resumeItemListStart
            \resumeItem{Built a serverless ETL pipeline in Python on AWS to ingest, validate, and deduplicate 5.6M records, cutting batch insert time 40\% via parallelized Lambda functions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, SQL, PHP} \\
     \textbf{Frameworks}{: Node.js, Express, FastAPI, React, Vite} \\
     \textbf{Cloud \& Databases}{: AWS (EC2, S3, RDS, Lambda, Glue, DynamoDB), Supabase, PostgreSQL, MySQL, DuckDB, Vector retrieval} \\
     \textbf{AI/ML}{: RAG pipelines, LLM fine-tuning (QLoRA), text-to-SQL, sentence embeddings, agentic workflows (n8n), PyTorch, scikit-learn}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
