%-------------------------
% Resume in LaTeX  --  Jake's Resume (Overleaf), MIT License
% https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Dhruvkumar Patel} \\ \vspace{1pt}
    \small (672) 553-1105 $|$ \href{mailto:dhruvv.patel@outlook.com}{\underline{dhruvv.patel@outlook.com}} $|$
    \href{https://www.linkedin.com/in/dhruvkumarpatell/}{\underline{LinkedIn}} $|$
    \href{https://github.com/pateldhruvkumar}{\underline{GitHub}} $|$
    \href{https://dhruvvkumarpatel.vercel.app/}{\underline{Portfolio}} $|$
    Vancouver, BC
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{An AI/ML engineer with a passion for agentic GenAI systems, LLM orchestration, and production-grade ML pipelines. Has built autonomous AI agents and secure RAG systems, fine-tuned Llama models to lift answer accuracy 15\%, and deployed scalable AWS infrastructure. Seeking a machine learning engineer role building generative AI products and MLOps platforms.}
  \vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Vancouver, BC}
      {Master of Professional Studies, Data Analytics (AI/ML Concentration)}{Jan 2025 -- Jun 2026}
    \resumeSubheading
      {Uka Tarsadia University}{Gujarat, India}
      {Bachelor of Technology, Information Technology (Graduated with Distinction)}{Aug 2019 -- Feb 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vault AI}{Remote}
      {Software Developer}{Jun 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Engineered an autonomous Due Diligence Agent that orchestrates multi-source web research to synthesize credit risk and legal compliance into production-ready PDF reports for private credit firms.}
        \resumeItem{Architected an AI-powered client intake portal for natural-language analytics and automated extraction from unstructured PDFs, built on Supabase and serverless Edge Functions for real-time processing.}
        \resumeItem{Built secure RAG pipelines over 100+ confidential documents with vector retrieval, ensuring enterprise-grade data privacy and reliable grounding for complex inquiries.}
        \resumeItem{Fine-tuned Llama models with QLoRA on domain-specific terminology, improving answer accuracy 15\% on internal evaluations.}
      \resumeItemListEnd
    \resumeSubheading
      {Dots N Key}{Surat, India}
      {Software Developer}{Dec 2022 -- Jul 2024}
      \resumeItemListStart
        \resumeItem{Boosted query performance 60\% on the SONAR POS platform by leading the full MySQL to AWS RDS migration, eliminating single-point-of-failure risk and unlocking production-grade scalability for high-traffic retail operations.}
        \resumeItem{Maintained 99.9\% system uptime by deploying cloud infrastructure on AWS EC2 and S3 with real-time monitoring dashboards, catching and resolving production incidents before end-user impact.}
      \resumeItemListEnd
    \resumeSubheading
      {Northeastern University}{Vancouver, BC}
      {Operations Data Assistant}{Jan 2026 -- Jun 2026}
      \resumeItemListStart
        \resumeItem{Diagnosed and rewrote an inefficient cost-calculation query in the operations database, correcting pricing logic and cutting university order spend by thousands of dollars annually.}
        \resumeItem{Maintained data accuracy and integrity across a 1,000+ student records database, supporting operations reporting and daily workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-Powered Seaweed Market Intelligence Dashboard} $|$ \emph{LLM Text-to-SQL, Embeddings, FastAPI}}{Apr 2026 -- Jun 2026}
          \resumeItemListStart
            \resumeItem{Engineered a text-to-SQL chat assistant on FastAPI and DuckDB where Qwen3.6-35B (via OpenRouter) generates queries against a 27,000-row dataset, grounded in the live schema, retrieved entities, and few-shot examples.}
            \resumeItem{Enforced SQL safety in three layers (parser validation, write-statement blocks, and up to 3 error-feedback retries), plus an enrichment LLM pass that summarizes results and selects a chart type, degrading to a plain table on failure.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Vancouver International Airport (YVR) Charging Forecast} $|$ \emph{Python, Streamlit, XGBoost, LightGBM}}{Jan 2026 -- Apr 2026}
          \resumeItemListStart
            \resumeItem{Engineered a Weighted Ensemble forecasting model (Random Forest, XGBoost, LightGBM) on 33 derived time, lag, flight, and weather features, hitting 84.7\% accuracy and a 28\% MAE reduction over a 2-month baseline for a 260-vehicle electric fleet.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Kahoot Bot -- Agentic AI Automation} $|$ \emph{Python, n8n, REST APIs}}{Aug 2025}
          \resumeItemListStart
            \resumeItem{Shipped an automated AI quiz system with n8n orchestrating 3 open-source APIs, hitting 90\% accuracy while cutting inference costs 60\% via optimized call sequencing; placed 2nd of 15+ teams at Northeastern's Agentic AI 2.0 Hackathon.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, JavaScript, TypeScript, PHP} \\
     \textbf{Frameworks \& Tools}{: FastAPI, React, Node.js, Express, Streamlit, Git, CI/CD, n8n, Power BI} \\
     \textbf{Cloud \& Databases}{: AWS (EC2, S3, Lambda, Glue, RDS, DynamoDB), Supabase, MySQL, MongoDB, DuckDB} \\
     \textbf{AI/ML}{: LLM orchestration, RAG, QLoRA fine-tuning, prompt engineering, agentic workflows, embeddings, PyTorch, scikit-learn, XGBoost, LightGBM}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
