%-------------------------
% Cover letter in LaTeX -- one page, clean business-letter style.
% Tailored for: Sobeys -- Machine Learning Engineer (2026-07-07)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}         % paragraph spacing instead of indents
\usepackage[english]{babel}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\pagestyle{empty}

\begin{document}

%---------- SENDER (from master-personal-info.md) ----------
\begin{center}
    {\Large \scshape Dhruvkumar Patel}\\[2pt]
    \small Vancouver, BC $|$ (672) 553-1105 $|$ \href{mailto:dhruvv.patel@outlook.com}{dhruvv.patel@outlook.com} $|$
    \href{https://www.linkedin.com/in/dhruvkumarpatell/}{LinkedIn} $|$ \href{https://dhruvvkumarpatel.vercel.app/}{Portfolio}
\end{center}

\vspace{8pt}
July 7, 2026

\vspace{4pt}
Hiring Team\\
Sobeys, Enterprise Data and Advanced Technology

\vspace{8pt}
Dear Hiring Team,

For the past year I have been building the exact kind of autonomous, tool-using agents your Enterprise Data and Advanced Technology team is standing up, so the Machine Learning Engineer role caught my attention immediately. Doing that work for a business that reaches millions of Canadian shoppers every day, where an agent's output shows up in real customer engagement and store operations, is a much bigger canvas than the problems I have worked on so far, and it is the one I want next.

At Vault AI I engineered an autonomous Due Diligence Agent that runs multi-source web research on its own and turns credit-risk and legal-compliance findings into production-ready reports, and a Multi-Company Financial Comparison Agent that cut manual comparison effort by 60\%. Underneath both, I built secure RAG pipelines over 100+ confidential documents using vector retrieval and sentence embeddings to keep the LLM's answers grounded, and I fine-tuned Llama models with QLoRA to lift answer accuracy 15\% on domain terminology. That is compound, retrieval-grounded agent work end to end. I have built it with n8n orchestration and custom LLM pipelines rather than LangGraph specifically, and picking up LangGraph to formalize what I already do is a fast step, not a new skill.

The retail and production side of the role also fits how I have worked. At Dots N Key I led a full MySQL to AWS RDS migration for a high-traffic retail POS platform that boosted query performance 60\%, and kept 99.9\% uptime on AWS EC2 and S3 with real-time monitoring. That is the same instinct your team needs: models and agents that stay maintainable and reliable in production, not just in a notebook. I am comfortable extending that foundation to MLOps tooling like MLflow and Databricks, and I am glad to work hybrid from the Toronto COLAB office.

I would welcome the chance to talk about how my agentic AI and production engineering experience can help the team ship intelligent systems that move customer engagement and sales for Sobeys. Thank you for your consideration.

\vspace{8pt}
Sincerely,\\
Dhruvkumar Patel

\end{document}
